---
title: "Evaluate lidar-based tree crown segmentation algorithms"
author: "Ben Weinstein"
date: "4/20/2018"
output: 
  html_document:
    toc: true
    number_sections: true
---

```{r,warning=F,message=F}
library(dplyr)
library(knitr)
library(maptools)
library(rgdal)
library(TreeSegmentation)
library(sp)
library(ggplot2)
library(rgl)
library(clue)
library(lidR)
knit_hooks$set(webgl = hook_webgl)
opts_chunk$set(warning=F,message=F)

#set color ramp for treeID
col = pastel.colors(200)

#set data paths
path_to_tiles="../data/2017/Lidar/cropped_"

#set cores
cores<-4
#cores<-15
```

# Load in ground-truth
```{r,results='hide'}
shps<-list.files("../data/ITCs/test/",pattern=".shp",full.names = T)
itcs<-lapply(shps,readOGR,verbose=F)

names(itcs)<-sapply(itcs,function(x){
  id<-unique(x$Plot_ID)
  return(id)
  })
```

# Example Pipeline

## Read in Data
```{r,webgl=TRUE}
ground_truth<-itcs[[9]]
fname<-get_tile_filname(ground_truth)
tile<-readLAS(paste("../data/2017/Lidar/cropped_",fname,sep=""))
tile@crs<-CRS("+init=epsg:32617")
plot(tile)
```

## Confirm overlap

```{r}
plot(extent(tile),col='red')
plot(extent(ground_truth),col='blue',add=T)
```

## Compute Segmentation

```{r}
silva<-silva2016(tile=tile,output="all")
dalponte<-dalponte2016(tile=tile,output="all")
li<-li2012(tile=tile,output="all")
watershed_result<-watershed(tile=tile,output="all")
```

## View 3d segmentation

```{r,webgl=TRUE}
plot(silva$tile,color="treeID",col=col)
```

### Overlay ground truth and predictions

```{r}
plot(silva$convex)
plot(ground_truth,col='red')
plot(silva$convex,add=T)
#plot(dalponte$convex,add=T)
```

### CHM versus predicted polygons

```{r}
chm=canopy_model(silva$tile)
plot(chm,ext=extent(ground_truth))
plot(ground_truth,add=T,col='red')
plot(silva$convex,add=T)
```

Okay that's not great, but let's keep going for the moment.

### Compare Methods

Silva v Dalponte
```{r}
plot(chm,ext=extent(ground_truth))
plot(silva$convex,add=T)
plot(dalponte$convex,add=T,col=rgb(0,0,255,20,maxColorValue=255))
```

Li versus watershed

```{r}
plot(chm,ext=extent(ground_truth))
plot(li$convex)
plot(watershed_result$convex,add=T,col=rgb(0,0,255,20,maxColorValue=255))
```

##Compute consensus

```{r}
ptlist<-list(silva=silva$tile,li=li$tile,dalponte=dalponte$tile,watershed=watershed_result$tile)
system.time(consensus_result<-consensus(ptlist=ptlist,method="majority"))
consensus_polygons<-get_convex_hulls(consensus_result,consensus_result@data$treeID)
plot(consensus_polygons,col=rgb(0,0,255,20,maxColorValue=255))
paste(length(consensus_polygons),"consensus clusters found")
```

### View consensus segmentation

```{r,webgl=TRUE}
#plot(consensus_result,color="treeID",col=col)
```

### Compare Consensus

```{r,eval=F}
plot(silva$convex)
plot(dalponte$convex)
plot(li$convex)
plot(consensus_polygons,add=T,col=rgb(0,0,255,40,maxColorValue=255))
```

How many tree predictions?

```{r}
library(pander)
unique_total<-sapply(c(ptlist,consensus_result),function(x) length(unique(x@data$treeID)))
df<-data.frame(Algorthm=c(names(ptlist),"consensus"),Total_Trees=as.numeric(unique_total))
pandoc.table(df,style="rmarkdown")
```

## Assign Trees

Each tree is assigned based on the maximum overlap. Pairwise membership is done using a Hungarian Algorithm. See clue::solve_LSAP.

```{r}
assignment<-assign_trees(ground_truth,prediction=silva$convex)
```

## Calculate Intersection over union

```{r}
#loop through assignments and get jaccard statistic for each assignment pair
statdf<-calc_jaccard(assignment=assignment,ground_truth = ground_truth,prediction=silva$convex)
ggplot(statdf) + geom_histogram(aes(IoU)) + labs(x="Intersection over union") + theme_bw()
mean(statdf$IoU)
median(statdf$IoU)
```

# As a wrapper for one tile, multiple methods, and consensus
```{r,eval=F}
results<-evaluate(ground_truth=itcs[[1]],algorithm = c("silva","dalponte","li"),path_to_tiles=path_to_tiles,compute_consensus = F,plot_results=T)

if(!is.null(results)){
  ggplot(results,aes(y=IoU,x=Method)) + geom_boxplot() + theme_bw()
results %>% group_by(Method) %>% summarize(mean=mean(IoU),median=median(IoU))
}
```

# Parallel wrapper across all tiles

```{r,eval=T}
system.time(results_all<-evaluate_all(itcs=itcs,algorithm = c("dalponte","li","watershed","silva"),path_to_tiles=path_to_tiles,cores=cores,extra=F,compute_consensus=F))

#plot results
ggplot(results_all,aes(y=IoU,x=Method)) + geom_boxplot() + theme_bw()

#Compute test statistics
test_statistic<-results_all %>% group_by(Method) %>% summarize(mean=mean(IoU),median=median(IoU)) %>% mutate(Date=format(Sys.time(), "%m/%d/%y %H:%M:%S"))
test_statistic
```

```{r}
write.table(test_statistic,"Results/results.csv",append = T,col.names = F,sep=",")
```

