---
title: "Extract Trees"
author: "Ben Weinstein"
date: "4/20/2018"
output: 
  html_document:
    toc: true
    number_sections: true
editor_options: 
  chunk_output_type: console
---

# Aim

* Generate predicted tree crowns based on lidar-based unsupervised segmentations
* Write training data in h5 format containing data and label

```{r setup, include=FALSE,warning=FALSE,message=F}
library(TreeSegmentation)
library(rgl)
library(knitr)
library(ggplot2)
library(dplyr)
library(rgdal)
library(lidR)
knit_hooks$set(webgl = hook_webgl)
opts_chunk$set(echo = TRUE)
```


# Get list of tiles

```{r}
site="NIWO"
las<-list.files(path="../data/NeonTreeEvaluation/NIWO/plots/",full.names=T,pattern =".laz")
epsg_df<-data.frame(site=c("SJER","TEAK","NIWO","MLBS"),epsg=c("32611","32611","32613","32618"))

#set epsg
epsg_numeric<-epsg_df[epsg_df$site %in% site,"epsg"]

```

# Example segmentation

```{r}
silva<-run_silva2016(path=las[10],epsg_numeric = epsg_numeric)
silva$tile@data %>% group_by(Classification,treeID) %>% summarize(n=n()) %>% summarize(median(n))
tile<-readLAS(las[10])
tile <- ground_model(tile)
chm<-canopy_model(tile)
```

```{r}
plot(chm)
plot(silva$convex,add=T)
```

```{r}
ind_trees<-extract_trees(algorithm = c("silva"),las=las,output="las", epsg_numeric = epsg_numeric)
```

Let's look at couple outputs from each tile

```{r}
sample_tree<-function(x){
  s<-x[[sample(length(x),1)]]
}
```

## Silva Method

```{r,webgl=TRUE}
a<-sample_tree(ind_trees[[sample(length(ind_trees),1)]][[1]])
a@data$Classification
plot(a,color="Classification",size=3)
```

```{r,webgl=TRUE}
a<-sample_tree(ind_trees[[sample(length(ind_trees),1)]][[1]])
a@data$Classification
plot(a,color="Classification",size=3)
```

```{r,webgl=TRUE}
a<-sample_tree(ind_trees[[sample(length(ind_trees),1)]][[1]])
a@data$Classification
plot(a,color="Classification",size=3)
```

## Li Method
```{r,webgl=TRUE}
a<-sample_tree(ind_trees[[sample(length(ind_trees),1)]][[2]])
a@data$Classification
plot(a,color="Classification",size=3)
```

```{r,webgl=TRUE}
a<-sample_tree(ind_trees[[sample(length(ind_trees),1)]][[2]])
a@data$Classification
plot(a,color="Classification",size=3)
```

```{r,webgl=TRUE}
a<-sample_tree(ind_trees[[sample(length(ind_trees),1)]][[2]])
a
a@data$Classification
plot(a,color="Classification",size=3)
```

What is the average number of points in segmented lidar clouds

```{r}
num_points<-unlist(lapply(ind_trees,function(x){sapply(x,function(y){sapply(y,function(z) nrow(z@data))})}))
qplot(num_points)
quantile(num_points)

#which.max(num_points)
#biggest<-ind_trees[["../data/2017/Lidar//OSBS_001.laz"]][["silva"]][[57]]
#plot(biggest,color="Classification",size=3)
```

What is the distribution of area covered by lidar clouds

```{r}
area_lidr<-unlist(lapply(ind_trees,function(x){sapply(x,function(y){sapply(y,area)})}))
qplot(area_lidr)
```

